Target Speaker Extraction using Discrete Representations from Self-Supervised Models and Language Models \thanks{Identify applicable funding agency here. If none, delete this.}

### 2024-09-03 src/paper.tex
update

Discretization methods have been studied for speech enhancement \cite{selm} and blind speech separation \cite{dasb}, however, this approach has been rarely for target speaker extraction. TokenSplit \cite{tokensplit} needs the transcript of the speech to achieve satisfying results. In 
real life, however, speech is rarely provided with its transcript.

>>>>

Discretization methods have been studied for speech 
enhancement \cite{selm} and blind speech separation \cite{dasb}, however, this approach has 
been rarely studied for target speaker extraction. TokenSplit \cite{tokensplit} utilizes 
Large Language Model to do blind speech separation instead of target speaker extraction. 
Also, it  needs the 
transcript of the speech to achieve satisfying results. In 
real life, however, speech is rarely provided with its transcript.
